% !TEX root = ./main.tex
\begin{acknowledgments}

Coming into this research topic with a background in physics, I was met with an array of interdisciplinary subjects and concepts that have proved essential to this work. I owe a tremendous deal of gratitude to my advisor Professor Nicole Riemer for not only teaching me so much of what I have learned over the course of my Masters thesis, but also for allowing and encouraging me to explore my intellectual curiosity and passion. I would also like to thank my other committee members, Professor Matthew West and Professor Larry Di Girolamo, for their contributions, insight, and guidance. Whether in the classroom, office hours, or in meetings, I am grateful for the many opportunities to learn from you all. 

I also wish to thank my lab group members for discussions and collaborations which have made this work possible. In particular, I would like to thank Matin Mohebalhojeh for our many discussions of spatial heterogeneity and for allowing me to collaborate on a paper summarizing the metric Matin developed. Additionally, I wish to thank Jeff Curtis for generously offering his time in answering countless questions about WRF, PartMC, and related subjects. 

I am grateful to the University of Illinois Department of Climate, Meteorology, and Atmospheric Sciences faculty and staff for fostering a truly unique and supportive learning environment. 

Beyond the professional realm, there are many friends and family who have been so encouraging throughout this process and for whom I am deeply grateful. In particular, I wish to thank my family and my partner Valerie for always supporting me.  

Funding for this research was provided by the Office of Science Biological and Environmental Research program, U.S. Department of Energy under Grant DE-SC0022130. 

\end{acknowledgments}